Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-01 Article/article.tex
tikz diagram for static schedule

\end{itemize}
\todo[inline]{SKumar: equivalent tikz figure}
\begin{tabular}{|l|l|l|}
\hline
Task & Comm Time & Comp Time\\ \hline
A & 3 & 2\\ \hline
B & 1 & 3\\ \hline
C & 4 & 4\\ \hline
D & 2 & 1\\ \hline
\end{tabular}
	\begin{figure}[htb]
	\centering
%% 	\subfloat[Optimal schedule]{
		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1, every node/.style={scale=1}]
		\node(t1) at (0,0) {};       		
		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};

		\node[below right=0cm and 0cm of b11.south east, draw, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b12) {$B$};

		\node[above right=0cm and 0cm of b11.south east, draw, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};

		\node[below right=0cm and 0cm of c11.south east, draw, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c12) {$C$};

		\node[above right=0cm and 0cm of c11.south east, draw, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};

		\node[below right=0cm and 0cm of c12.north east, draw, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};

		\node[above right=0cm and 0cm of a11.south east, draw, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};

		\node[below right=0cm and 0cm of a12.north east, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};

@@

%%		\draw[->] ([xshift=-0.1cm, yshift=-1cm] b11.south west)--([xshift=13cm, yshift=-1cm] b11.south west);
		\tikzstyle{legend}=[below=0.25, anchor=mid] 	
		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
             -- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
             -- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
             -- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
             -- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
             -- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
             -- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
             -- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.5] {$10$}
             -- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
             -- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}                                      
              --([shift={(13, -0.65)}] t1.mid) node[right,scale=0.5] {$t$};

@@

 		\node(t1) at ([shift={(0, -2)}] t1.mid) {};       		
		 \node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};

>>>>

\end{itemize}
\todo[inline]{SKumar: equivalent tikz figure}
\begin{tabular}{|l|l|l|}
\hline
Task & Comm Time & Comp Time\\ \hline
A & 3 & 2\\ \hline
B & 1 & 3\\ \hline
C & 4 & 4\\ \hline
D & 2 & 1\\ \hline
\end{tabular}
	\begin{figure}[htb]
	\centering
%% 	\subfloat[Optimal schedule]{
		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.5, every node/.style={scale=0.5}]
		\tikzstyle{legend}=[below=0.25, anchor=mid] 	
		\node(t1) at (0,0) {};

	    \node[above right=0.8cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=13cm, draw=white, fill=white](IMC) {$Infinite Memory Capacity$};

		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b11) {$B$};

		\node[below right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b12) {$B$};

		\node[above right=0cm and 0cm of b11.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c11) {$C$};

		\node[below right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c12) {$C$};

		\node[above right=0cm and 0cm of c11.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a11) {$A$};

		\node[below right=0cm and 0cm of c12.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a12) {$A$};

		\node[above right=0cm and 0cm of a11.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};

		\node[below right=0cm and 0cm of a12.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};

@@

%%		\draw[->] ([xshift=-0.1cm, yshift=-1cm] b11.south west)--([xshift=13cm, yshift=-1cm] b11.south west);

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
             -- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
             -- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
             -- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
             -- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
             -- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
             -- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
             -- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.5] {$10$}
             -- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
             -- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}                                      
              --([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

@@

 		\node(t1) at ([shift={(0, -3)}] t1.mid) {};   
	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=13cm, draw=white, fill=white](MC) {$Memory Capacity=6$};

   		\node(t1) at ([shift={(0, -0.8)}] t1.mid) {};                		
		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};

		\node[below right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b22) {$B$};

		\node[above right=0cm and 0cm of b21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c21) {$C$};

		\node[below right=0cm and 0cm of c21.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c22) {$C$};

		\node[above right=0cm and 0cm of c22.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a21) {$A$};

		\node[below right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a22) {$A$};

		\node[above right=0cm and 0cm of a21.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d11) {$D$};

		\node[below right=0cm and 0cm of d11.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d12) {$D$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$}                                      
		-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.5]{$15$}
	  	-- ([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

		\foreach \x in {0, 1, 4, 5, 9, 12, 14, 15} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

%% schedule of third heuristic		
   		\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b31) {$B$};

		\node[below right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b32) {$B$};

		\node[above right=0cm and 0cm of b31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d31) {$D$};

		\node[below right=0cm and 0cm of b32.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d32) {$D$};

		\node[above right=0cm and 0cm of d31.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a31) {$A$};

		\node[below right=0cm and 0cm of a31.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a32) {$A$};

		\node[above right=0cm and 0cm of a32.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c31) {$C$};

		\node[below right=0cm and 0cm of c31.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c32) {$C$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.5] {$3$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.5] {$6$}         
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}                                      
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5]{$12$} 
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$}
		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

		\foreach \x in {0, 1, 3, 4, 5, 6, 8, 12, 16} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$BDAC$};

%% schedule of fourth heuristic		
		\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c41) {$C$};

		\node[below right=0cm and 0cm of c41.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c42) {$C$};

		\node[above right=0cm and 0cm of c41.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b41) {$B$};

		\node[below right=0cm and 0cm of c42.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b42) {$B$};

		\node[above right=0cm and 0cm of c42.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a41) {$A$};

		\node[below right=0cm and 0cm of a41.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a42) {$A$};

		\node[above right=0cm and 0cm of b42.north east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d41) {$D$};

		\node[below right=0cm and 0cm of d41.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d42) {$D$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.5] {$13$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$} 
		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

		\foreach \x in {0, 4, 5, 8, 11, 13, 14} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$CBAD$};

%% schedule of fifth heuristic		
		\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d51) {$D$};

		\node[below right=0cm and 0cm of d51.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d52) {$D$};

		\node[above right=0cm and 0cm of d51.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b51) {$B$};

		\node[below right=0cm and 0cm of b51.south east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b52) {$B$};

		\node[above right=0cm and 0cm of d52.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a51) {$A$};

		\node[below right=0cm and 0cm of a51.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a52) {$A$};

		\node[above right=0cm and 0cm of a52.north east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c51) {$C$};

		\node[below right=0cm and 0cm of c51.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c52) {$C$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.5] {$2$}
		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.5] {$3$}
		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.5] {$6$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}         
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$} 
		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

		\foreach \x in {0, 2, 3, 6, 8, 12, 16} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$DBAC$};

%% schedule of sixth heuristic		
		\node(t1) at ([shift={(0, -1.8)}] t1.mid) {};                		
		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c61) {$C$};

		\node[below right=0cm and 0cm of c61.south east, minimum height=0.5cm, minimum width=4cm,draw,fill=white](c62) {$C$};

		\node[above right=0cm and 0cm of c62.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](a61) {$A$};

		\node[below right=0cm and 0cm of a61.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](a62) {$A$};

		\node[above right=0cm and 0cm of a61.south east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b61) {$B$};

		\node[below right=0cm and 0cm of a62.north east, minimum height=0.5cm, minimum width=3cm,draw,fill=white](b62) {$B$};

		\node[above right=0cm and 0cm of b61.south east, minimum height=0.5cm, minimum width=2cm,draw,fill=white](d61) {$D$};

		\node[below right=0cm and 0cm of b62.north east, minimum height=0.5cm, minimum width=1cm,draw,fill=white](d62) {$D$};

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}
		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.5] {$13$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$}
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$} 
		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.5] {$17$}  
		--([shift={(17.1, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

		\foreach \x in {0, 4, 8, 11, 12, 13, 14, 16, 17} \draw ([shift={(\x, -0.61)}] t1.mid) -- ([shift={(\x, -0.69)}] t1.mid);

		\node[above left=-0.15cm and 1cm of t1.mid, scale=1, rotate=0] {$CABD$};
